Sample Length at Which Block Bootstrapping is Effective for Estimation of Parameter of Time Series

### 2023-02-09 Manuscript/manuscript.tex
Manuscript Update

\begin{abstract}
Block bootstrapping is a method that can be used for estimating a parameter of a time
series. It involves splitting a series into blocks (in order to account for the temporal dependence
factor) and re-sampling the blocks to create many new bootstrapped pseudo-samples of the time series.
This method becomes more effective as the length of the time series increases. 
The question that this study seeks to answer is what sample length is necessary for the block
bootstrap method to be effective in estimating a parameter of a time
series.

\bigskip
\noindent\sc{Keywords}:
block bootstrap;
\end{abstract}

@@

Block bootstrapping is a widely used method in Statistics. The concept for block 
bootstrapping was developed independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
\citet{kunsch1989jackknife}. \citet{radovanov2014comparison} It has been applied to a variety of 
different domains such 
as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
situations in which there is temporal dependence within a population, and the goal is the estimation or testing a hypothesis about a parameter. Assuming that the sample is infinitely 
large, the method will work perfectly. However, for a finite sample size, the method will 
not work as well as expected. In the context of planning an applied 
statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to work at an acceptable level.

\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes. \citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for estimation using the bootstrap method (simple resampling with no blocks involved). 
\citet{goncalves2005bootstrap} found that standard error estimates from block bootstrapping small 
samples may be significantly more accurate than inference from closed-form asymptotic estimates. That study focused on the estimation of a coefficient parameter within the context of linear regression. Still, the block bootstrap percentile confidence intervals under-covered the parameter even for n = 1024.

The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
is an effective method for estimating a parameter in the context of a time series. The method is effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals created from samples of the same size recover the parameter. This study will focus on estimating parameters of an AR(1) process with several types of confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} which will be reviewed in Section 2.

@@

Block bootstrapping is a method that can be used to estimate a parameter of an AR(1) process. Suppose that one wants to estimate a parameter or parameters $\theta$ of an AR(1) process: 
\[X_{t} = \mu + \epsilon_{t} + \phi*X_{t-1}.\] The first step is to generate a sample of length $n$ from the process. An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean $\bar\theta_n^*$ of many (typically 1000) replicate $\hat\theta_n^*$ can also be computed. Lastly, for each $\hat\theta_n^*$, $\delta = \hat\theta_n^* - \hat{\theta}_{n}$ and $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.

In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement. In the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size. The block should be of size $l$ large enough to include time dependence, yet small enough to include some variance. As $n$ increases, an ideal $l$ should also increase, but the ratio of $l$ to $n$ should decrease. To achieve this, $l$ is often assigned a value as a function of $n$. A common function that is considered the best by much previous literature is $l = \lceil = n^{1/3} \rceil$. \citep{buhlmann1999block} A bootstrapped sample is created by taking a sample of $n / l$ blocks with replacement to create a new pseudo-sample of size $n$. The designer of the study can choose whether the blocks overlap or not. If the blocks can never overlap, it is called a non-moving block bootstrap. In this case, the original sample is split evenly into $n / l$ blocks, and the same number of blocks are sampled with replacement to create a bootstrapped pseudo-sample. If the blocks do overlap, it is called a moving block bootstrap. $n / l$ samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks. $\hat\theta_n^*$ is computed from the pseudo-sample. This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.

In this study, 1000 bootstrapped $\hat\theta_n^*$ were created for each simulation. Using this distribution of $\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be created. The most simplistic method for constructing this interval is the percentile confidence interval. For a parameter $\theta$, the percentile $1 - \alpha$/2 \% confidence interval takes the form: 
\[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\] 
Another method is the bias-corrected and accelerated 
(BCA) $1 - \alpha$/2 \% confidence interval, which takes the form: 
\[ [\hat\theta_{n, \alpha_1}^*,\hat\theta_{n, \alpha_2}^*].\] 
$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and $z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} + z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of ...

	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals around either $\hat{\theta}_{n}$ or $\bar\theta_n^*$. To do this, the distribution of $\delta$ or $\delta^*$ should be considered. A percentile interval centered around $\hat{\theta}_{n}$ takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
A percentile interval centered around $\bar\theta_n^*$ takes the form: 
\[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\]
An alternative is an interval of the form:
\[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] 
which is equivalent to:
\[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] 
and therefore is also equivalent to:
\[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] 
Thus, the interval is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.

This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
A BCA interval centered around $\bar\theta_n^*$ takes the form: 
\[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\]
An alternative is an interval of the form:
\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}],\]

@@

R has a built in function that allows you to simulate an AR(1) process, for which one can set the theoretical $\phi$. For the purposes of this study, $\mu$ should be fixed at 0, and the standard deviation of the process $\sigma_{x}$ should be fixed at 1. By default, the standard deviation of the error term $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:

\[X_{t} = \epsilon_{t} + \phi*X_{t-1}.\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi*X_{t-1})\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2*\sigma^2_{x}\]
\[\sigma^2_{x}(1 - \phi^2) = \sigma^2_{\epsilon}\]
\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \phi^2}\]

The only parameter of the AR(1) process that was varied was $\phi$, as the temporal dependence affects the performance of block bootstrap. $\phi$ = 0 (a standard normal distribution), 0.2, and 0.4 were used in this study.

As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. In this study, $\theta$ is composed of the target parameters $\mu$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, six block bootstrap 95\% confidence intervals can be constructed for each target parameter: ....

Each of these 18 intervals either recovers $\theta$ or does not. Remember that 95\% of a certain type of 95\% confidence intervals constructed from samples of the same $n$ should recover $\theta$. To see if this is approximately the case, one can run 1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers $\theta$ can be recorded.

If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = 100, 200, 300, 400, and 500$ were used in this study.

@@

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_0}
  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly at $n = 500$. All but three intervals seem to cover $\phi$ generally well for $n = 300$. The alternate percentile interval slightly under-covers $\phi$ for all sample lengths observed. The BCA interval centered around $\hat{\theta}_{n}$ significantly under-covers $\phi$ and the percentile interval centered around $\bar\theta_n^*$ over-covers $\phi$. All intervals seem to cover $\sigma$ generally well for n = 500 except for the $\hat{\theta}_{n}$-centered BCA interval, which slightly under-covers $\sigma$ for all sample lengths observed, and the  $\bar\theta_n^*$-centered BCA interval, which also under-covers $\sigma$.}
  \label{fig:plot_0}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.2}
  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly at $n = 300$ and $n = 400$. The alternate percentile interval and the $\hat{\theta}_{n}$-centered percentile interval cover $\phi$ well at $n = 500$. The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed. The alternate BCA interval under-covers $\phi$, and its performance deteriorates as $n$ increases, as does the $\bar\theta_n^*$-centered percentile interval but with lower coverage rates and more noticeable deterioration. The $\hat{\theta}_{n}$-centered BCA interval significantly under-covers $\phi$, although there is no clear deterioration.}
  \label{fig:plot_.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.4}
  \caption{At $\phi = .4$,}
  \label{fig:plot_.4}
\end{figure}

@@

This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger. When implementing the block bootstrap method to estimate the mean or variance of an autoregressive process, the non-moving method and moving method perform about the same. However, when estimating the AR(1) coefficient, the non-moving method performs noticeably worse than the moving method, which still covers the coefficient poorly when theta is greater than 0. Whereas the performance improves as sample length increases when the target is the mean or variance, the performance decays as sample length increases when the target is the AR(1) coefficient.

>>>>

\begin{abstract}
Block bootstrapping is a method that is useful for estimating a parameter of a time
series. Theoretically, the method will work perfectly given an infinitely large sample of the time series.
It is necessary to know how large of a finite sample is required to for block bootstrap estimation to work. Before this study, there have been no investigations into this problem in the literature. The aim of this study is to answer this question by simulating replications of block bootstrap interval estimations of a parameter of a time series, and recording the rate at which the parameter is recovered by each replicate interval. The sample length required for acceptable performance is unsurprisingly found to be dependent on the type of interval construction and the series' level of temporal dependence.

\bigskip
\noindent\sc{Keywords}:
simulation;
\end{abstract}

@@

Block bootstrapping is a widely used method in Statistics. The concept for block 
bootstrapping was developed independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
\citet{kunsch1989jackknife}. \citet{radovanov2014comparison} It has been applied to a variety of 
different domains such 
as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
situations in which there is temporal dependence within a population, and the goal is to estimate or test a hypothesis about a parameter. Assuming that the sample is infinitely 
large, the method should work perfectly. However, for a finite sample size, the method may 
not work as well as expected. In the context of planning an applied 
statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to perform at an acceptable level.

\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrapping (simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes. \citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrapping.
\citet{goncalves2005bootstrap} found that standard error estimates from block bootstrapping small 
samples may be significantly more accurate than inference from closed-form asymptotic estimates. That study focused on the estimation of a coefficient parameter within the context of linear regression. Still, the block bootstrap percentile confidence intervals under-covered the parameter even for n = 1024.

While the aforementioned studies have looked into the necessary sample size for various bootstrap methods, the goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
is an effective method for estimating a parameter specifically in the context of a time series. The method can be considered effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals created from samples of the same size recover the parameter. This study will focus on estimating parameters of an AR(1) process with two types of confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} which will be reviewed in Section 2.

@@

Block bootstrapping is a method that can be used to estimate a parameter of serially dependent data. Suppose that one wants to estimate a parameter or parameters $\theta$ of a population. The first step is to generate a sample of length $n$ from the population. An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean $\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ can also be computed. Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.

In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement. However, in the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size. The block should be of size $l$ large enough for each pseudo-sample to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample. Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is often assigned a value as a function of $n$. A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$. \citep{buhlmann1999block} The designer of the study can choose whether the blocks overlap or not. If the blocks do not overlap, it is called a non-moving block bootstrap. In this case, the original sample is split evenly into blocks, which will then be resampled to create new pseudo-samples. If the blocks do overlap, it is called a moving block bootstrap. Blocks are resampled randomly from the original sample, but they do not have to be from a set of evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$. If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ and one block of size $(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.

In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block bootstrap estimation. Using this distribution of $\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be constructed. The most simplistic method for constructing this interval is the percentile confidence interval. For a parameter $\theta$, the percentile $1 - \alpha$/2 \% confidence interval takes the form: 
\[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\] 
Another method is the bias-corrected and accelerated 
(BCA) $1 - \alpha$/2 \% confidence interval, which takes the form: 
\[ [\hat\theta_{n, \alpha_1}^*,\hat\theta_{n, \alpha_2}^*].\] 
$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and $z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} + z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of $\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the original sample computed without the $i^{th}$ block.

	Both of these intervals work well when attempting to recover the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals $\hat{\theta}_{n}$. To do this, the distribution $\delta^*$ should be considered. A percentile interval centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]

%A percentile interval centered around $\bar\theta_n^*$ ($CI_{\bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\] An alternative is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] which is equivalent to: \[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] and therefore is also equivalent to: \[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] Thus, the interval ($CI_{\hat{\theta}_{n}, \bar\theta_n^*}$) is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.

This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
%A BCA interval centered around $\bar\theta_n^*$ ($CI_{BCA, \bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\] An alternative (($CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$) is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}]\]

Thus, there are two types of intervals used for estimation in this study: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$. Note that both of these intervals are centered around $\hat{\theta}_{n}$ and asymmetric.

@@

Base R has a built in function arima.sim that allows one to simulate an AR(1) process, for which one can set the theoretical $\phi$. By default, the mean of the process $\mu$ is 0 and the standard deviation of the error term $\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard deviation of the process $\sigma_{x}$ should be controlled at 1. The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:

\[X_{t} = \epsilon_{t} + \phi X_{t-1}.\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1})\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x}\]
\[\sigma^2_{x}(1 - \phi^2) = 1\]
\[\sigma_{x}\sqrt{1 - \phi^2} = 1\]

The experimental factor of this study was $\phi$, as the temporal dependence affects the performance of block bootstrap. $\phi = -0.4 -0.2,$ and $0$ (a standard normal distribution)$, 0.2, and 0.4$ were used in this study.

As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. This method can be simulated with the tsboot function from the boot R package. In this study, $\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, two types of block bootstrap 95\% confidence intervals can be constructed for each target parameter: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.

Each of these 6 intervals either recovers $\theta$ or does not. Remember that 95\% of many of a certain type of 95\% confidence intervals constructed from samples of the same $n$ should recover $\theta$. To see if this is generally or approximately the case, one can run 1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers $\theta$ can be recorded.

If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = $100, 200, 300, 400, and 500, 600, 700 were used in this study.

@@

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.4}
  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear pattern of deterioration of coverage.}
  \label{fig:plot_n.4}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.2}
  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as $n = 100$. Both intervals seem to cover $\sigma$ generally well, although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.  $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_n.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_0}
  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ seems to cover $\phi$ generally well at $n = 400$, but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the method's performance seems to improve as $n$ increases.}
  \label{fig:plot_0}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.2}
  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as $n = 300$. Both intervals seem to cover $\sigma$ generally well, although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.4}
  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear sign of coverage deterioration, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.4}
\end{figure}

Only $CI_{\hat{\theta}_{n}}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that this interval should be used as opposed to $CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$.

@@

The motivation for the study is the idea that block bootstrap procedure will perfectly estimate a parameter of a time series given an infinitely large sample. The goal for this study was to find what is a good enough finite sample length for block bootstrap estimation to recover the parameter of a time series at an acceptable rate. Assuming that $CI_{\hat{\theta}_{n}}$ is used, The results of this study suggest that even for estimating $\mu$, an $n$ of around 500 may be necessary if $\phi$ is unknown. An $n$ of around 400 may be necessary to estimate $\sigma$ is $\phi$ is unknown. If $\phi$ is already known, a lesser $n$ may be adequate to estimate these parameters. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. This information could prove to be useful for researching using block bootstrap estimation of time series in domains such as econometrics. Future studies could investigate the sample size needed to estimate or test an hypothesis about other forms of serially dependent data such as an MA process.
